sampbias, a method for quantifying geographic sampling biases in species distribution data

### 2020-09-15 04_appendix_S1.Rmd
tidy up github

---
title: "sampbias, a method for quantifying geographic sampling biases in species distribution data"
subtitle: "Appendix S1 - Supplementary Figure"
author: "Alexander Zizka, Alexandre Antonelli, Daniele Silvestro"
output: rmarkdown::pdf_document
header-includes: |
    \usepackage{float}
    \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

```{r, echo = FALSE, fig.height = 7, fig.cap="The bias weights ($w$) of the empirical analyses of records from mammals from Borneo (6262 records, www.gbif.org, 2016, https://doi.org/10.15468/dl.7fg4zx) in comparison to ten simulated datasets of the same size with randomly picked locations across Borneo (no bias)."}

@@

plo <- bind_rows(sim) %>%
  mutate(ID = paste("Replicate_", as.character(ID), sep = "")) %>% 
  mutate(type = "Simulated (no bias)") %>% 
  dplyr::select(contains("w"), ID, type) %>%
  pivot_longer(cols = contains("w_"), names_to = "bias",
                 values_to = "posterior_estimate") %>%
    mutate(bias = gsub("w_", "", .data$bias)) %>% 
  bind_rows(emp)

@@

```{r, echo = FALSE, fig.cap="The bias weights ($w$) quantifying the effects of each bias factor estimated from data sets with differing density of occurrence records across the study area. Datasets generated by down-sampling the empirical example dataset of mammal occurrences on Borneo (www.gbif.org,  2016, https://doi.org/10.15468/dl.7fg4zx)."}
ggplot(data = dat)+
  geom_boxplot(aes(x = bias, 
                   y = posterior_estimate,
                 fill = as.factor(records_area),
                 color = as.factor(records_area)))+
  ylab("Posterior weight")+
  xlab("Bias factor")+
  scale_fill_viridis(discrete = TRUE, name = "Records per\n10,000 sqkm")+
  scale_color_viridis(discrete = TRUE, name = "Records per\n10,000 sqkm")+
  theme_bw()
```

```{r, out.width = "6in", fig.cap = "Projected bias surface for the distribution data of mammals from Borneo (www.gbif.org, 2016, https://doi.org/10.15468/dl.7fg4zx), at different levels of downsampling, from a random replicate. The plotted extent is adapted to the study area, which may not cover the entire island for rarified datasets with few records (A) and B))"}

>>>>

---
title: "sampbias, a method for quantifying geographic sampling biases in species distribution data"
subtitle: "Appendix S1 - Supplementary Figures"
#author: "Alexander Zizka, Alexandre Antonelli, Daniele Silvestro"
output: rmarkdown::pdf_document
header-includes: |
    \usepackage{float}
    \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

```{r, echo = FALSE, fig.height = 7, fig.cap="The bias weights ($w$) of the empirical analyses of records from mammals from Borneo (6262 records, www.gbif.org, 2016, https://doi.org/10.15468/dl.7fg4zx) in comparison to ten simulated data sets of the same size with randomly picked locations across Borneo (no bias)."}

@@

plo <- bind_rows(sim) %>%
  mutate(ID = paste("Rep_", as.character(ID), sep = "")) %>% 
  mutate(type = "Simulated (no bias)") %>% 
  dplyr::select(contains("w"), ID, type) %>%
  pivot_longer(cols = contains("w_"), names_to = "bias",
                 values_to = "posterior_estimate") %>%
    mutate(bias = gsub("w_", "", .data$bias)) %>% 
  bind_rows(emp)

@@

```{r, echo = FALSE, fig.cap="The bias weights ($w$) estimated from data sets with differing density of occurrence records across the study area. Datasets generated by down-sampling the empirical example dataset of mammal occurrences on Borneo (www.gbif.org,  2016, https://doi.org/10.15468/dl.7fg4zx)."}
ggplot(data = dat)+
  geom_boxplot(aes(x = bias, 
                   y = posterior_estimate,
                 fill = as.factor(records_area),
                 color = as.factor(records_area)))+
  ylab("Posterior weight")+
  xlab("Bias factor")+
  scale_fill_viridis(discrete = TRUE, name = "Records per\n10,000 sqkm")+
  scale_color_viridis(discrete = TRUE, name = "Records per\n10,000 sqkm")+
  theme_bw()
```

```{r, out.width = "6in", fig.cap = "Projected bias surface for the distribution records of mammals from Borneo (www.gbif.org, 2016, https://doi.org/10.15468/dl.7fg4zx). A) - D) Different levels of random downsampling. The plotted extent is adapted to the study area, which may not cover the entire island for rarified datasets with few records (A) and B))"}
